---
title: "Task 21"
output: 
  html_document:
    keep_md: TRUE
    code_folding: hide
---
### Loading in Kroger Stock Prices
```{r}
library(tidyquant)
library(tidyverse)
library(dplyr)
library(lubridate)
library(timetk)
library(dygraphs)


x1 <- 'KR'
end <- today() - days(1)
start <- end - years(5)

x1_prices <- tq_get(x1, get = 'stock.prices', from = start, to = end)
head(x1_prices)

kr_stock_prices <- x1_prices %>% 
  select(symbol, date, adjusted) %>% 
  pivot_wider(names_from = symbol, values_from = adjusted) %>% 
  tk_xts(date_var = date)
```
### Plot for Kroger Stock Prices
```{r}
dygraph(kr_stock_prices, main = 'Kroger Stock Prices for the Past 5 Years') %>%
  dySeries(fillGraph = TRUE) %>% 
  dyHighlight(highlightCircleSize = 5., 
              highlightSeriesBackgroundAlpha = 0.2,
              hideOnMouseOut = FALSE) %>% 
  dyOptions(axisLineColor = "black",
            gridLineColor = "black") %>% 
  dyRangeSelector(dateWindow = c("2015-11-04","2020-11-04")) 

```


### If $10,000 Were Invested 5 Years Ago
```{r}
two_years <- x1_prices %>% 
  filter(date >= '2018-11-04')

head(two_years)

kr_stock_prices_twoyears <- two_years %>% 
  select(symbol, date, adjusted) %>% 
  pivot_wider(names_from = symbol, values_from = adjusted) %>% 
  tk_xts(date_var = date)

dygraph(kr_stock_prices_twoyears, main = 'If $10,000 Were Invested 2 Years Ago in Kroger') %>% 
  dySeries(fillGraph = TRUE) %>% 
  dyHighlight(highlightCircleSize = 5) %>% 
  dyRebase(value = 10000) %>% 
  dyAnnotation("2019-03-08", text = 'A', tooltip = 'Walmart and Target Post Best Numbers of Decade') %>% 
  dyAnnotation("2020-03-05", text = 'B', tooltip = 'National Pandemic Declared') %>% 
  dyRangeSelector(dateWindow = c("2018-11-04", "2020-11-04"))
```


### Report
The first graph is of Kroger's stock prices over the past 5 years. I decided to include the fill feature becuase I believe it looks better. I changed the highlighting dot to size 5 given its over a long period of time and the feature makes it easier to see where your curser is on the graph. 

The second graph is if you were to invest $10,000 into Kroger exactly 2 years ago to the day. They tend to decrease at point A. After doing some reasearch, I suspect that this is the point of time large retailers such as Target and Walmart took off with online grocery shopping. Point B is the national pandemic. Kroger flucuated a lot during this time, but has seemed to continue to increase over the big picture.
