---
title: "Case Study 11"
output: 
  html_document:
    keep_md: TRUE
    code_folding: hide
---
## Loading in Libraries
```{r}
library(tidyquant)
library(tidyverse)
library(dplyr)
library(lubridate)
library(timetk)
library(dygraphs)
```

## Stock Data
```{r}
tickers_today <- c("CXW", "F", "GM", "JCP", "KR", "WDC", "NKE","T", "WDAY", "WFC", "WMT")
start <- today() - years(5)

todays_prices <- tq_get(tickers_today, get = 'stock.prices', from = start)
head(todays_prices)

matrix_prices <- todays_prices %>% 
  select(symbol, date, adjusted) %>% 
  pivot_wider(names_from = symbol, values_from = adjusted) %>% 
  tk_xts(date_var = date)
head(matrix_prices)

```

## Overall Stock Prices Past 5 Years
```{r}
dygraph(matrix_prices, main = 'Tickers Today') %>%
  dySeries(fillGraph = FALSE) %>% 
  dyHighlight(highlightCircleSize = 5., 
              highlightSeriesBackgroundAlpha = 0.2,
              hideOnMouseOut = FALSE) %>% 
  dyOptions(axisLineColor = "black",
            gridLineColor = "black") %>% 
  dyRangeSelector() 

```

## Percent Change
```{r}
perc_change <- todays_prices %>% 
  group_by(symbol) %>% 
  mutate(percent_change_total = (adjusted/adjusted[1]-1)*100)

head(perc_change)

matrix_prices_perc <- perc_change %>% 
  select(symbol, date, percent_change_total) %>% 
  pivot_wider(names_from = symbol, values_from = percent_change_total) %>% 
  tk_xts(date_var = date)

dygraph(matrix_prices_perc, main = 'Percent Change') %>%
  dySeries(fillGraph = FALSE) %>% 
  dyHighlight(highlightCircleSize = 5., 
              highlightSeriesBackgroundAlpha = 0.2,
              hideOnMouseOut = FALSE) %>% 
  dyOptions(axisLineColor = "black",
            gridLineColor = "black") %>% 
  dyRangeSelector()

```

## If $25,000 Were Invested 5 Years Ago
```{r}
dygraph(matrix_prices, main = 'If $25,000 Were Invested Into Each 5 Years Ago') %>% 
  dySeries(fillGraph = FALSE) %>% 
  dyHighlight(highlightCircleSize = 5., 
              highlightSeriesBackgroundAlpha = 0.2,
              hideOnMouseOut = FALSE) %>%
  dyRebase(value = 25000)
```

## Volume
```{r}
volumes <- todays_prices %>% 
  group_by(symbol, date, volume) %>% 
  select(symbol, date, volume)
head(volumes)

ggplot() +
  geom_line(data = volumes, mapping = aes(x = date, y = volume, color = symbol)) +
  facet_wrap(~symbol, nrow = 3) +
  labs(x = 'Date', y = 'Volume', title = 'Volumes For Each Stock') +
  theme_bw() +
  theme(legend.position = 'none')


```

## Analysis
I chose to make graphs that showed the overall stock price, the percent change, if I had invested $25,000 into each stock, and the volume over the past 5 years. I chose to make interactive graphs for the stock price, percent chagne, and the if I had invested graphs because it makes it easeir to read, as well as shows you the numbers and dates. For the volumes, I made it using ggplot2() and faceted by the symbols.

After analyzing the data, I would invest in WMT, GM, WFC, NKE, and WDC. I would evenly distrubte the 25,000 dollars amongst the stocks. An investor would use the volume of a stock and compare it to the price change. If the price is going up as well as the volume, people are wanting to buy the stock, and vice versa.