---
title: "Case Study 12"
output: 
  html_document:
    keep_md: TRUE
    code_folding: hide
---

## Loading in Data
```{r}
library(tidyverse)
library(USAboundaries)
library(USAboundariesData)
library(dplyr)
library(ggplot2)
library(sf)



permits <- read_csv(url('https://github.com/WJC-Data-Science/DTS350/raw/master/permits.csv'))
head(permits)

permits <- permits %>% 
  select(state, StateAbbr,county, countyname, variable, year, variable, value)
head(permits)

```

## Acquiring Data
```{r}
state_totals <- permits %>% 
  group_by(state, county, year) %>% 
  summarise(total = mean(value, na.rm = TRUE))
head(state_totals)



state_totals <- state_totals %>% 
  rename(
    countyfp = county,
    statefp = state
  )

```

## US States and Counties
```{r}
us_states <- us_states()
head(us_states)

us_counties <- us_counties()
us_counties$statefp <- as.numeric(us_counties$statefp)
us_counties$countyfp <- as.numeric(us_counties$countyfp)

final <- merge(state_totals, us_counties, all = TRUE, by = c("countyfp","statefp"))

```

## 1986
```{r}
final1 <- state_totals %>% 
  filter(year == 1986)


final1g <- merge(final1, us_counties, all = TRUE, by = c("statefp","countyfp"))

ggplot() +
  geom_sf(data = final1g, aes(geometry = geometry,  fill = total)) +
  coord_sf(xlim = c(-125, -65), ylim = c(25, 50)) +
  labs(title = '1986') +
  theme_bw()
```

## 1991
```{r}
final2 <- state_totals %>% 
  filter(year == 1991)

final2g <- merge(final2, us_counties, all = TRUE, by = c("statefp","countyfp"))

ggplot() +
  geom_sf(data = final2g, aes(geometry = geometry,  fill = total)) +
  coord_sf(xlim = c(-125, -65), ylim = c(25, 50)) +
  labs(title = '1991') +
  theme_bw()
```

## 2005
```{r}
final3 <- state_totals %>% 
  filter(year == 2005)

final3g <- merge(final3, us_counties, all = TRUE, by = c("statefp","countyfp"))


ggplot() +
  geom_sf(data = final3g, aes(geometry = geometry,  fill = total)) +
  coord_sf(xlim = c(-125, -65), ylim = c(25, 50)) +
  labs(title = '2005') +
  theme_bw()
```

## 2009
```{r}
final4 <- state_totals %>% 
  filter(year == 2009)

final4g <- merge(final4, us_counties, all = TRUE, by = c("statefp","countyfp"))


ggplot() +
  geom_sf(data = final4g, aes(geometry = geometry,  fill = total)) +
  coord_sf(xlim = c(-125, -65), ylim = c(25, 50)) +
  labs(title = '2009') +
  theme_bw()
```

## Analysis
These graphics show the permits by county for the entire United States. It doesn't look so good because states like California dominate and tip the scale. Because of this it is difficult to see the change in the data, however we know that from looking at the data previously that permits peaked in 1986 with a decline in 1991. And then of course peaked in 2005 and had a major dip to 2009. I decided to go by county because I thought it would be more interesting, and while it is hard to see with a small graph, it is very clear when you blow up the image.