---
title: "Task 20"
output: 
  html_document:
    keep_md: TRUE
    code_folding: hide
---
### Loading in the Stocks 
```{r}
library(tidyquant)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(lubridate)


## My Stocks
target <- tq_get("TGT", get = 'stock.prices', from = '2019-10-1', to = '2020-11-3')
microsoft <- tq_get("MSFT", get = 'stock.prices', from = '2019-10-1', to = '2020-11-3')
acadia <- tq_get('ACAD', get = 'stock.prices', from = '2019-10-1', to = '2020-11-3')

my_stocks <- bind_rows(target, microsoft, acadia)
my_stocks$data <- 'mine'


## Morehouse Stocks
zoom <- tq_get('ZM', get = 'stock.prices', from = '2019-10-1', to = '2020-11-3' )
nike <- tq_get("NKE", get = 'stock.prices', from = '2019-10-1', to = '2020-11-3')
apple <- tq_get("AAPL", get = 'stock.prices', from = '2019-10-1', to = '2020-11-3')

morehouse_stocks <- bind_rows(zoom, nike, apple)
morehouse_stocks$data <- 'his'

```
### Overall Plot
```{r}
ggplot() +
  geom_line(data = my_stocks, mapping = aes(x = date, y = close, color = symbol)) +
  geom_line(data = morehouse_stocks, mapping = aes(x = date, y = close, color = symbol)) +
  facet_wrap(~data) +
  labs(x = 'Date', y = 'Closing Price', title = 'Overall Stocks') +
  theme_bw()

```
### Percent Change
```{r}
my_stocks <- my_stocks %>% 
  group_by(symbol) %>% 
  mutate(percent_change = (close/lead(close)-1)*100,
         percent_change_total = (close/close[1]-1)*100)

morehouse_stocks <- morehouse_stocks %>% 
  group_by(symbol) %>% 
  mutate(percent_change = (close/lead(close)-1)*100,
         percent_change_total = (close/close[1]-1)*100)

by_day_percent_change <- ggplot() +
  geom_line(data = my_stocks, mapping = aes(x = date, y = percent_change, color = symbol)) +
  geom_line(data = morehouse_stocks, mapping = aes(x = date, y = percent_change, color = symbol)) +
  facet_wrap(~data) +
  labs(x = 'Date', y = 'Percent Change', title = 'Percent Change By Day') +
  theme_bw()
by_day_percent_change

total_change <- ggplot() +
  geom_line(data = my_stocks, mapping = aes(x = date, y = percent_change_total, color = symbol)) +
  geom_line(data = morehouse_stocks, mapping = aes(x = date, y = percent_change_total, color = symbol)) +
  facet_wrap(~data) +
  labs(x = 'Date', y = 'Percent Change', title = 'Total Percent Change') +
  theme_bw()
total_change  
```
### Sum of Percent Change by Day
### Blue is me and Red is Morehouse
```{r}
morehouse_percent_change <- morehouse_stocks %>%
  group_by(data, date) %>% 
  summarise(total = sum(percent_change, na.rm = TRUE))

my_percent_change <- my_stocks %>% 
  group_by(data, date) %>% 
  summarise(total = sum(percent_change, na.rm = TRUE))

ggplot() +
  geom_line(data = morehouse_percent_change, mapping = aes(x = date, y = total), color = 'red') +
  geom_line(data = my_percent_change, mapping = aes(x = date, y = total), color = 'blue') +
  labs(x = 'Date', y = 'Percent Change', title = 'Sum of Percent Change By Day') +
  theme_bw()

```
### Sum of Percent Change Total
### Blue is me and Red is Morehouse
```{r}
morehouse_pc_total <- morehouse_stocks %>%
  group_by(data, date) %>% 
  summarise(total = sum(percent_change_total, na.rm = TRUE))

my_pc_total <- my_stocks %>% 
  group_by(data, date) %>% 
  summarise(total = sum(percent_change_total, na.rm = TRUE))


ggplot() +
  geom_line(data = morehouse_pc_total, mapping = aes(x = date, y = total), color = 'red') +
  geom_line(data = my_pc_total, mapping = aes(x = date, y = total), color = 'blue') +
  labs(x = 'Date', y = 'Percent Change', title = 'Sum of Percent Change Total') +
  theme_bw() +
  theme(legend.key = )

```
### Report
I chose to show an overall graph in order to see the total picture between my stocks and Morehouses. It was pretty obvious from that point on the Morehouse would win given he chose Zoom (I think this is unfair). I then calculated the total percent change by day and when you view this graph it may be misleading that I may have a chance to win, but once you view the total summed percent change it is obvious that Morehouse beat me. However, you can see that priar to Covid, I had the lead and then Zoom took off making it an easy win for Morehouse.
