---
title: "Case Study 5"
output: 
  html_document:
    keep_md: TRUE
---
## FiveThirtyEight Article
In this article, they show the 33,000 gun deaths that happen each year and in which categories they fit in to. The categories are suicide, homocide, accidental/undetermined, mass shootings, terrorism, and shootings of police officers

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)

download.file("https://raw.githubusercontent.com/fivethirtyeight/guns-data/master/full_data.csv", "full_data.csv")

full_data <- read_csv("full_data.csv")

head(full_data)
view(full_data)


```
## Graphic to mimic article's findings
```{r}
male_suicide = full_data %>% 
  filter(intent == "Suicide" & age >= 45)

ggplot(data = male_suicide) +
  geom_bar(mapping = aes(x = month, fill = sex), position = 'dodge') +
  facet_wrap(~month)

```
This is a grpahic that reflects how the article stated that the male population far out weighs the females population in regards to total amount of suicides.



### Customer's Concerns
```{r}
homicide <- full_data %>% 
  filter(intent == "Homicide", age <= 30, race == "Black")

ggplot(data = homicide) +
  geom_bar(mapping = aes(x = month, fill = sex), position = 'dodge')+
  facet_wrap(~month) +
  ggtitle("Homicide Rates") +
  theme_bw()




suicide <- full_data %>% 
  filter(intent == "Suicide", age <= 20, race == "White")

ggplot(data = suicide) +
  geom_bar(mapping = aes(x = month, fill = sex), position = 'dodge') +
  facet_wrap(~month) +
  ggtitle("Suicide Rates") +
  theme_bw()


undetermined <- full_data %>% 
  filter(intent == "Undetermined")


ggplot(data = undetermined) +
  geom_bar(mapping = aes(x = month, fill = sex), position = 'dodge') +
  facet_wrap(~month) +
  ggtitle("Undetermined Rates") +
  theme_bw()
```
## Homicide Image
Looking at the data for homicides througout the months, I would recommmend the company to focus on the younger black populations during the summer and winter months

## Suicide Image
Looking at the data for suicides rates for the white population below 20 years old, I would recommend the company focuses on the spring months, especially April

## Undetermined Image
If the company was interested in focusing on undetermined cases, then they should devote their time in November for males and September for females.

