---
title: "Task 13"
output: 
  html_document:
    keep_md: TRUE
    code_folding: hide
---

## Loading Data & Plots
```{r}
library(tidyverse)
library(haven)
library(readr)
library(readxl)
library(downloader)


data_rds  <- read_rds(url("https://github.com/WJC-Data-Science/DTS350/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.RDS"))

data_dta  <- read_dta("https://github.com/WJC-Data-Science/DTS350/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.dta")

data_cvs  <- read_csv("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.csv")

sav <- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.sav", sav, mode = "wb")
dfsav <- read_sav(sav)


xlsx <- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.xlsx",xlsx, mode = "wb")
dfxlsx <- read_xlsx(xlsx)


all_equal(data_dta, dfsav, convert = TRUE)
all_equal(data_dta, dfxlsx, convert = TRUE)
all_equal(data_dta, data_rds, convert = TRUE)
all_equal(data_rds, dfsav, convert = TRUE)
all_equal(data_rds, dfxlsx, convert = TRUE)
all_equal(dfxlsx, dfsav, convert = TRUE)


view(data_rds)

data_dta2 <- data_dta %>% 
  separate(contest_period, into = c("Month/Month", "Year_end"), sep = -4)

head(data_dta2)

data_dta3 <- data_dta %>% 
  separate(contest_period, into = c("Month/Month", "Year_end"), sep = -4) %>% 
  group_by(Year_end, variable) %>% 
  summarise(Average = mean(value, na.rm = TRUE))

data_dta3


## Graphics
plot1 <- ggplot(data = data_dta2) +
  geom_boxplot(mapping = aes(x = Year_end, y = value)) +
  labs(x = "Year_end", y = "Values", color = "Variable", title = "Boxplot")

plot1

plot2 <- ggplot(data = data_dta3) +
  geom_line(mapping = aes(x = Year_end, y = Average, color = variable, group = variable)) +
  labs(x = "Year_end", y = "Values", color = "Variable", title = "Average Plot")

plot2


plot3 <- ggplot(data = data_dta2) + 
  geom_jitter(mapping = aes(x = Year_end, y = value, color = variable))+
  labs(x = "Year_end",
       y = "Value",
       color = "Variable",
       title = "Jitter Plot")

plot3


plot4 <- ggplot(data = data_dta3) +
  geom_line( mapping = aes(group = variable, x = Year_end , y = Average, color  = variable), size = 1.5)+
  geom_jitter( data = data_dta2, mapping = aes(x = Year_end, y = value, color = variable))+
  labs(x = "Year_end",
       y = "Value",
       color = "Variable",
       title = "Jitter and Line Plot")

plot4

```
- Plot 1 is a boxplot that is determined by year and value of return. Based on the plot, it appears that the data was most spread out in the early and late 1990s.

- Plot 2 shows the average collected by year and grouped by the variables. The three variables have similiar trends, but DART decreased from 1996 to 1997 while the other two increased

- Plot 3 is a jitter plot that shows the data by year and grouped by the variables. It shows that the variable DIJA is the most consistent

- Plot 4 is a combination of Plot 2 and Plot 3





## Tidy Data & Saving RDS
```{r}
data_dta4 <- data_dta2 %>% 
  separate("Month/Month", into = c("month_begin", "month_end"), sep = "-")

data_dta4


saveRDS(data_dta4,"data_dta4.rds")
```
## 6 Month Returns Based on Year
```{r}
data_dta5 <- data_dta4 %>% 
  group_by(Year_end) %>% 
  summarise(sum_collected = sum(value, na.rm = TRUE))

data_dta5

plot6 <- ggplot(data = data_dta5) +
  geom_point(mapping = aes(x = Year_end, y = sum_collected), color = 'blue') +
  geom_path(mapping = aes(x = Year_end, y = sum_collected, group = 1), color = 'blue') +
  labs(x = 'Year Ended',
       y = 'Total Collected',
       title = 'Six Months Returns by Year') +
  theme_bw()

plot6
```
- Plot 6 shows the sums for the 6 month collection periods when grouped by year. It shows the total collections dipped from 1992 to 1994 and again after 1997.

## Final Table
```{r}
data_dta6 <- data_dta4 %>% 
  mutate(month_end = replace(month_end, month_end == "Dec.", "December")) %>%
  mutate(month_end = replace(month_end, month_end == "Febuary", "February")) %>%
  select(-c(month_begin)) %>%
  filter(variable == "DJIA") %>%
  pivot_wider(names_from = Year_end, values_from = value) %>%
  select(-c(variable)) %>%
  mutate(month_end = replace(month_end, month_end == "January", 1)) %>%
  mutate(month_end = replace(month_end, month_end == "February", 2)) %>%
  mutate(month_end = replace(month_end, month_end == "March", 3)) %>%
  mutate(month_end = replace(month_end, month_end == "April", 4)) %>%
  mutate(month_end = replace(month_end, month_end == "May", 5)) %>%
  mutate(month_end = replace(month_end, month_end == "June", 6)) %>%
  mutate(month_end = replace(month_end, month_end == "July", 7)) %>%
  mutate(month_end = replace(month_end, month_end == "August", 8)) %>%
  mutate(month_end = replace(month_end, month_end == "September", 9)) %>%
  mutate(month_end = replace(month_end, month_end == "October", 10)) %>%
  mutate(month_end = replace(month_end, month_end == "November", 11)) %>%
  mutate(month_end = replace(month_end, month_end == "December", 12)) 

data_dta6

data_dta6$month_end <- as.integer(data_dta6$month_end)  

data_dta6 <- data_dta6[order(data_dta6$month_end),]  

data_dta6  

data_dta7 <- data_dta6 %>%
  mutate(month_end = replace(month_end, month_end == 1,"January")) %>%
  mutate(month_end = replace(month_end, month_end == 2,"February")) %>%
  mutate(month_end = replace(month_end, month_end == 3,"March")) %>%
  mutate(month_end = replace(month_end, month_end == 4,"April")) %>%
  mutate(month_end = replace(month_end, month_end == 5,"May")) %>%
  mutate(month_end = replace(month_end, month_end == 6,"June")) %>%
  mutate(month_end = replace(month_end, month_end == 7,"July")) %>%
  mutate(month_end = replace(month_end, month_end == 8,"August")) %>%
  mutate(month_end = replace(month_end, month_end == 9,"September")) %>%
  mutate(month_end = replace(month_end, month_end == 10,"October")) %>%
  mutate(month_end = replace(month_end, month_end == 11,"November")) %>%
  mutate(month_end = replace(month_end, month_end == 12,"December"))  

head(data_dta7, 12) 
```

