---
title: "Case Study 7"
output: 
  html_document:
    keep_md: TRUE
    code_folding: hide
---
## Loading Data
```{r}
## Case Study 7

library(tidyverse)
library(haven)
library(readr)
library(readxl)
library(downloader)
library(measurements)

xlsx1 <- tempfile()
download("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/Height.xlsx", xlsx1, mode = 'wb')

ww_df <- read_xlsx(xlsx1, skip = 2)
ww_df
view(ww_df)

tidy_ww <- ww_df %>% 
  pivot_longer(c(`1800`:`2011`), names_to = 'Year_Real', values_to = 'height.cm')

tidy_ww


tidy_ww2 <- tidy_ww %>%
  separate(Year_Real, into = c("century", "decade", "year"), sep = c(-2,-1), remove = FALSE) 
tidy_ww2

tidy_ww2$Year_Real <- as.numeric(tidy_ww2$Year_Real)
tidy_ww2$century <- as.numeric(tidy_ww2$century)
tidy_ww2$decade <- as.numeric(tidy_ww2$decade)
tidy_ww2$year <- as.numeric(tidy_ww2$year)

ww_inches <- tidy_ww2 %>% 
  mutate(height.in = conv_unit(height.cm, 'cm', 'inch'))

ww_inches

ww_inches2 <- na.omit(ww_inches)

ww_inches2

tubheight <- ww_inches2[order(ww_inches2$Year_Real),]

head(tubheight)

###
height_dta2 <- read_dta("https://github.com/WJC-Data-Science/DTS350/raw/master/germanprison.dta")
height_dta2

height_dta <- read_dta("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/germanconscr.dta")
height_dta

height_csv <- read_csv("https://raw.githubusercontent.com/hadley/r4ds/master/data/heights.csv")
height_csv


sav1 <- tempfile()
download("https://www.ssc.wisc.edu/nsfh/wave3/NSFH3%20Apr%202005%20release/main05022005.sav", sav1, mode = 'wb')
height_sav <- read_sav(sav1)
height_sav  




library(foreign)

temp <- tempfile()
download("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/Heights_south-east/B6090.DBF", temp, mode = 'wb')
height_dbf <- read.dbf(temp)

height_dbf

```
## Cleaning Data
```{r}
## Clean DTA

dta1 <- height_dta %>% 
  select(bdec, height)

dta1

dta2 <- dta1 %>% 
  rename(birth_year = bdec) %>% 
  rename(height.cm = height)

dta2$height.in <- conv_unit(dta2$height.cm, 'cm', 'inch')

dta2 <- add_column(dta2,study = "GermanConscr")

dta2

## Clean DTA2

df1 <- height_dta2 %>% 
  select(bdec, height)
df1

df2 <- df1 %>% 
  rename(birth_year = bdec) %>% 
  rename(height.cm = height)


df2$height.in <- conv_unit(df2$height.cm, 'cm', 'inch')

df2 <- add_column(df2,study = "GermanPrison")

df2


#Clean DBF
clean_dbf <- height_dbf %>% 
  select(SJ, CMETER)

clean_dbf2 <- clean_dbf %>% 
  rename(birth_year = SJ) %>% 
  rename(height.cm = CMETER)

head(clean_dbf2)

clean_dbf2$height.in <- conv_unit(clean_dbf2$height.cm, 'cm','inch')

head(clean_dbf2)

clean_dbf2 <- add_column(clean_dbf2, study = "Southeast")

head(clean_dbf2)

## Clean CSV
clean_csv <- height_csv %>% 
  select(height)

clean_csv

clean_csv2 <- clean_csv %>% 
  rename(height.in = height)

head(clean_csv2)

clean_csv2$height.cm <- conv_unit(clean_csv2$height.in, 'inch','cm')

clean_csv2

clean_csv2 <- add_column(clean_csv2, birth_year = 1950)


head(clean_csv2)

clean_csv2 <- add_column(clean_csv2, study = 'BLS')

head(clean_csv2)

clean_csv2 <- clean_csv2 %>% 
  select(birth_year, height.cm, height.in, study)

clean_csv2

## Clean SAV
clean_sav <- height_sav %>% 
  select(DOBY, RT216F, RT216I)

clean_sav

clean_sav2 <- clean_sav %>% 
  mutate(height.in = ((RT216F*12) + RT216I))

clean_sav2

clean_sav3 <- clean_sav2 %>% 
  mutate(birth_year = 1900 + DOBY)

clean_sav3

clean_sav3 <- add_column(clean_sav3, study = 'Wisconsin')

clean_sav3

clean_sav3$height.cm <- conv_unit(clean_sav3$height.in, 'inch', 'cm')

clean_sav3
  
clean_sav4 <- clean_sav3 %>% 
  select(birth_year, height.in, height.cm, study)

clean_sav4

```
## Bind the Data
```{r}
height_df <- bind_rows(dta2, df2, clean_dbf2, clean_csv2, clean_sav4)

height_df  

getwd()

setwd("/Users/chaseelias/Documents/William Jewell/3.Jewell Junior/DTS 350/Eliasc/DTS350TemplateMaster/Week_08")

getwd()

saveRDS(tubheight, file = 'tubheight.Rds')
saveRDS(height_df, file = 'height_df.rds')
```
## Plots
```{r}
germany <- tubheight %>% 
  filter(`Continent, Region, Country` == "Germany")
germany

tub_data <- ggplot() +
  geom_point(data = tubheight, mapping = aes(x = Year_Real, y = height.in), color = 'white') +
  geom_point(data = germany, mapping = aes(x = Year_Real, y = height.in), color = 'red') +
  theme_dark()

tub_data

##
small_mult <- ggplot(data = height_df) +
  geom_point(mapping = aes(x = birth_year, y = height.in)) +
  facet_wrap(~study)

small_mult

wisc <- height_df %>% 
  filter(study == 'Wisconsin')


Wiscon <- ggplot(data = wisc) +
  geom_point(mapping = aes(x = birth_year, y = height.in)) +
  geom_smooth(mapping = aes(x = birth_year, y = height.in)) +
  theme_bw()

Wiscon


SE <- height_df %>% 
  filter(study == "Southeast")

southeast_trend <- ggplot(data = SE) +
  geom_point(mapping = aes(x = birth_year, y = height.in)) +
  geom_smooth(mapping = aes(x = birth_year, y = height.in)) +
  theme_bw()

southeast_trend


overall_trend <- ggplot(data = height_df) +
  geom_point(mapping = aes(x = birth_year, y = height.in, color = study)) +
  geom_smooth(mapping = aes(x = birth_year, y = height.in), color = 'red') +
  theme_bw()

overall_trend
```
The tub_data plot shows the tubheight dataset with Germany being highlighted in Red. The x axis is by decade and the y axis is by height in inches. You can see that Germany has a steady increase in height throughout the decades.

The Wiscon graphic shows the overall trend in the Wisconsin survey. It didn't appear to have an increasing trend line.

The southwest_trend flucuated a lot, but overall seemed to have an increasing trendline.

The overall_trend was surprising to me. It doesn't seem like the trendline goes up much at all over time. There are data points in the Wisconsin survey that need to be removed because they don't make sense.

Overall, the tub_data shows through Germany that people are increasingly getting taller, but the height_df shows no such trend.
